Two-Phase Commit Using Blockchain

### 2022-06-04 paper/paper.tex
Add total row to the table.
Order the citations.
Add ACM demo.

\documentclass[11pt,conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage[sort,nocompress]{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{textcomp}
\usepackage{url}
\usepackage{xcolor}
\usepackage[htt]{hyphenat}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

@@

\author{\IEEEauthorblockN{Benjamin Marks}
  \IEEEauthorblockA{\textit{Stanford University} \\
  benmarks@stanford.edu}
  \and
  \IEEEauthorblockN{Heron Yang}
  \IEEEauthorblockA{\textit{Stanford University} \\
  heronyang@stanford.edu}
  \and
  \IEEEauthorblockN{Yuewei Na}
  \IEEEauthorblockA{\textit{Stanford University} \\
  yueweina@stanford.edu}
}

@@

\begin{IEEEkeywords}
  Atomic Commit, Blockchain, Smart Contract, Distributed System, Database Transaction.
\end{IEEEkeywords}

@@

We define a transaction as a list of operations starting with \texttt{Begin} followed by multiple \texttt{Get} or \texttt{Put} and ending with \texttt{Commit}. The client creates a transaction and requests the coordinator to commit. The coordinator distributes the transaction to the corresponding cohorts to prepare and then offloads the remaining 2PC responsibility to the blockchain. Each cohort prepares the transaction locally, votes to the blockchain if ready, checks on the blockchain to see if a transaction should be committed, and finally commits the transaction to its database.

@@

\bibliographystyle{plain}
\bibliography{references}

\appendix
\label{appendix}
\begin{table}[hbtp]
  \centering
  \caption{Gas used, cost in ETH/USD per blockchain transaction for a successful 2PC commit with 2 cohorts. Data as of 2022/05/30.}
  \label{table:cost}
  \begin{tabular}{|l|c|c|c|}
    \hline
          & Gas Used (Gwei) &  Cost in ETH & Cost in USD \\
          \hline
    StartVoting &73441 &0.000073441 & 0.143\\
    \hline
    Vote 1 &56451	&0.000056451 &0.110\\
    \hline
    Vote 2 &39513 &0.000039513 &0.077\\
    \hline
  \end{tabular}
\end{table}
\end{document}
\endinput

>>>>

\documentclass[11pt,sigplan,screen,nonacm]{acmart}
% \documentclass[11pt,conference]{IEEEtran}
% \IEEEoverridecommandlockouts
% \usepackage[sort,nocompress]{cite}
\usepackage{natbib}
\setcitestyle{square, comma, numbers,sort&compress, super}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{textcomp}
\usepackage{url}
\usepackage{xcolor}
\usepackage[htt]{hyphenat}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

@@

\author{Benjamin Marks}
\affiliation{%
  \institution{Stanford University}
  \city{Stanford}
  \state{California}
  \country{USA}
}
\email{benmarks@stanford.edu}

\author{Heron Yang}
\affiliation{%
  \institution{Stanford University}
  \city{Stanford}
  \state{California}
  \country{USA}
}
\email{heronyang@stanford.edu}

\author{Yuewei Na}
\affiliation{%
  \institution{Stanford University}
  \city{Stanford}
  \state{California}
  \country{USA}
}
\email{yueweina@stanford.edu}

% \author{\IEEEauthorblockN{Benjamin Marks}
  % \IEEEauthorblockA{\textit{Stanford University} \\
  % benmarks@stanford.edu}
  % \and
  % \IEEEauthorblockN{Heron Yang}
  % \IEEEauthorblockA{\textit{Stanford University} \\
  % heronyang@stanford.edu}
  % \and
  % \IEEEauthorblockN{Yuewei Na}
  % \IEEEauthorblockA{\textit{Stanford University} \\
  % yueweina@stanford.edu}
% }

@@

% \begin{IEEEkeywords}
  % Atomic Commit, Blockchain, Smart Contract, Distributed System, Database Transaction.
% \end{IEEEkeywords}
\keywords{atomic commit, blockchain, smart contract, distributed system, database transaction}

@@

We define a transaction as a list of operations starting with \texttt{Begin()} followed by multiple \texttt{Get()} or \texttt{Put()} and ending with \texttt{Commit()}. The client creates a transaction and requests the coordinator to commit. The coordinator distributes the transaction to the corresponding cohorts to prepare and then offloads the remaining 2PC responsibility to the blockchain. Each cohort prepares the transaction locally, votes to the blockchain if ready, checks on the blockchain to see if a transaction should be committed, and finally commits the transaction to its database.

@@

\bibliographystyle{unsrt}
\bibliography{references}

\appendix
\label{appendix}
\begin{table}[hbtp]
  \centering
  \caption{Gas used, cost in ETH/USD per blockchain transaction for a successful 2PC commit with 2 cohorts. Data as of 2022/05/30.}
  \label{table:cost}
  \begin{tabular}{|l|c|c|c|}
    \hline
          & Gas Used (Gwei) &  Cost in ETH & Cost in USD \\
          \hline
    StartVoting &73441 &0.000073441 & 0.143\\
    \hline
    Vote 1 &56451	&0.000056451 &0.110\\
    \hline
    Vote 2 &39513 &0.000039513 &0.077\\
    \hline
    Total &169405 &0.000169405 &0.330\\
    \hline
  \end{tabular}
\end{table}
\end{document}
\endinput
